\subsection{Introduction to Sets}
\hspace*{1em}
In discrete math we work with some group of `things,' a thing or something
we fancily call an \textbf{object}. A group or categorization of objects is called a set.

\begin{Def}[Set]{def:set}
    Is a collection of objects.
\end{Def}

\noindent
\textbf{For Example:}
\begin{itemize}
    \item $S$ = The set of all students in a classroom.
    \item $A$ = The set of all vowels in the English alphabet.
    \item $\mathbb{Z}$ = The set of all integers.

\end{itemize}
Objects in a \textbf{set} are called \textbf{elements}.

\begin{Def}[Element]{def:element}
    An object that is a member of a given set.
\end{Def}

\noindent
To expand on the previous example:
\begin{itemize}
    \item $S = \{s_1, s_2, s_3\}$, where $s_1, s_2, s_3$ are students, elements of the set.
    \item $A = \{a, e, i, o, u\}$, where $a, e, i, o, u$ are elements.
    \item $\mathbb{Z} = \{\ldots, -3, -2, -1, 0, 1, 2, 3, \ldots\}$, elements of integer set.
\end{itemize}
Curly braces denote a set, commas separate elements, and
the `$...$' (ellipse) indicates an indefinite continuation, \underline{used only when the pattern \textbf{is clear.}}\\

\newpage

\noindent
There is also notation to denote members of a set.

\begin{Def}[Membership]{def:membership}
    If $x$ is an element of set $A$, $x \in A$.
    If $x$ is not an element of set $A$, $x \notin A$.
\end{Def}

\noindent
\textbf{For Example:} Given $A = \{a, e, i, o, u\}$,\\
$a \in A$, ``$a$ is an element of $A$,'' and
$b \notin A$, ``$b$ is not an element of $A$.''\\

\noindent
\textbf{Order nor repetition matter:}
\begin{itemize}
    \item $A = \{1, 2, 3\} = \{3, 2, 1\} = \{1, 2, 3, 3, 3, 3, 3\}$.
    \item $B = \{a, b, c\} = \{a, b, c, a, b, c\}$.
\end{itemize}

\begin{Def}[Properties of a Set]{def:set_props}
    \begin{itemize}
        \item The order of elements do not matter.
        \item Duplicate elements are not counted.
    \end{itemize}
\end{Def}


A subset is a set contained within another set. If the set $B$ is a subset of set $A$,
then every element in $B$ is also in $A$ as shown in Figure \ref{fig:subset}:


\begin{figure}[ht]
    \centering
    \hspace{5.5em}
    \begin{tikzpicture}
        % Set A
        \draw[fill=gray!12] (0,0) circle (2.6cm);
        \node at (-1,1.3) {$A$};

        % Set B
        \draw[fill=OliveGreen!20] (0.5,0) circle (1cm);
        \node at (0.5,0) {$B$};

        % Subset arrow
        \draw[->, thick] (1.5,0) -- (3.5,0);

        % Subset label
        \node at (4.16,0) {Subset};
    \end{tikzpicture}
    \caption{$B$ is a subset of $A$.}
    \label{fig:subset}
\end{figure}


\noindent
Written $B \subseteq A$ or $A \supseteq B$, similar to the less than or
equal to signs `$\leq$' and `$\geq$'.

\newpage

\begin{Def}[Subset]{def:subset}
    If every element in set $B$ is also in set $A$, then $B$ is a subset of $A$.\\
    Denoted: $B \subseteq A$ or $A \supseteq B$.
\end{Def}

\noindent
\textbf{For Example:}
\begin{itemize}
    \item $\{-1, 0\} \subseteq \{-1, 0, 1, 2, 3\}$
    \item $\{-1, 1, 3\} \subseteq \{-1, 0, 1, 2, 3\}$
    \item $\{-1, 0, 1, 2, 3\} \subseteq \{-1, 0, 1, 2, 3\}$
    \item $\{-1, 7\} \not\subseteq \{-1, 0, 1, 2, 3\}$
\end{itemize}

\underline{$\not\subseteq$ denotes `not a subset of.'}

\vspace{1em}

\noindent
A set with no elements is called the empty set.
\begin{Def}[Empty Set]{def:empty_set}
    Commonly denoted by $\emptyset$ or $\{\}$, refers to a collection with no objects.
\end{Def}


\noindent
\textbf{Questions:}
\begin{enumerate}
    \item How many elements are in the set  $\{\emptyset\}$?
    \item True or False: $\emptyset \subseteq \{\emptyset\}$.
    \item True or False: $\emptyset \in \{\emptyset\}$.
    \item True or False: $\emptyset \subseteq \emptyset$.
    \item True or False: $\emptyset \subseteq \mathbb{Z}$.
    \item True or False: $\emptyset \in \mathbb{Z}$.
\end{enumerate}
\begin{Tip}
    Mathematicians define things? So can you! Let's define a collection that
    infinitely repeats the string ``bees.'' We will fancily call it\\
    ``\textbf{Bioths Non-determinant Sequence},'' or a $\beta_{seq}$ for short.
    $$\beta_{seq} = \{\textnormal{``bees''}, \textnormal{``bees''}, \textnormal{``bees''}, \textnormal{``bees''},
        \textnormal{``bees''}, \textnormal{``bees''}, \ldots\}$$

    \noindent
    \textbf{Names are names}, no matter how fancy, they were labeled
    by another human, like you. They thought,... ``Damn, this would be a \textit{kick-ass} name.''\\
    Never be intimidated, complex ideas are just groupings of basic concepts.
\end{Tip}
\newpage
\noindent
\textbf{Answers:}
\begin{enumerate}
    \item 1 element, the empty set.
    \item True, the empty set is a subset of $\{\emptyset\}$.
    \item True, the empty set is an element of $\{\emptyset\}$.
    \item True, the empty set is a subset of itself.
    \item True, the empty set is a subset of all sets.
    \item False, the empty set is not an element of the integers.
\end{enumerate}

\vspace{2em}

\noindent
\begin{greenbox}
    \underline{\textbf{Why (1.):}} \textbf{A collection is an object}. The emptyset is a collection,
    a collection without objects. Likewise, a house is still a house without furniture.\\

    \noindent
    \underline{\textbf{Why (5.):}} Take sets $A=\{\}$ and $B=\{1,2,3\}$\\
    By definition of a subset, every element in $A$ must be in $B$. It's difficult to
    argue elements in $A$ are indeed in $B$, but it's undeniable that elements in $A$ are not in $B$.
    Since our statement cannot be denied, it's \underline{\textbf{Vacuously true}}.\\
\end{greenbox}


\noindent
\hrulefill\\

\noindent
Say we have an empty box. How many objects do we have? \textbf{Zero}.\\
Put an empty box inside our original box. How many objects now? \textbf{One}!


\begin{figure}[ht]
    $\hspace{.2cm}$
    \begin{tikzpicture}
        % Set A
        \draw[fill=gray!20] (0,0) rectangle (2.6cm,2.6cm);
        \node at (-.5,2) {$Box_1$};

        % arrow
        \draw[->, thick] (3,1.3) -- (4.8,1.3);

    \end{tikzpicture}
    \begin{tikzpicture}
        % Set A
        \draw[fill=gray!20] (0,0) rectangle (2.6cm,2.6cm);
        \node at (-.5,2) {$Box_1$};

        % Set B
        \draw[fill=OliveGreen!20] (1,1) rectangle (.1cm,.1cm);
        \node at (1.5,0.5) {$Box_2$};

        \hfill
    \end{tikzpicture}
    \caption{\centering \underline{$Box_1$ contains 1 object,} which is $Box_2$, an empty box. Hence $\quad$
        $Box_1$ represents $\{\{\}\}$ or $\{\emptyset\}$.}
    \label{fig:empty_box}
\end{figure}

\noindent
\hrulefill\\

\newpage
\noindent
Counting the number of elements in a set is called the \textbf{cardinality} of the set.
\begin{Def}[Cardinality]{def:cardinality}
    The number of elements in a set.\\
    Denoted over a set $A$ as $|A|$.
\end{Def}

\noindent
\textbf{For Example:}
\begin{itemize}
    \item $A = \{1, 2, 3\}$, $|A| = 3$.
    \item $B = \{a, e, i, o, u\}$, $|B| = 5$.
    \item $\mathbb{Z}$ the set of all integers, $|\mathbb{Z}| = \infty$.
\end{itemize}

\noindent
\textbf{Questions:}\\
What are the cardinalities of the following sets?
\begin{enumerate}
    \item $|\{1,2,3\}|$
    \item $|\emptyset|$
    \item $|\{\}|$
    \item $|\{\emptyset\}|$
    \item $|\{1,\{2,3\}\}|$
    \item $|\{1,2,2,3,3,3\}|$
\end{enumerate}

\vspace{1em}

\noindent
\textbf{Try to think about the answer before looking at the solution.}\\
Things stick when you struggle.\\

\begin{Tip}
    Whenever you approach a problem, always break things down into simple components.
    ``What defines a set? What defines an element? What defines a subset? What defines cardinality?''\\
\end{Tip}

\noindent
\textbf{Answers:}
\begin{enumerate}
    \item 3
    \item 0
    \item 0
    \item 1
    \item 2
    \item 3
\end{enumerate}

\newpage

\noindent
Explicitly defining a set, say $\{1, 2, 3, ...\}$, is called \textbf{set-roster notation}.\\
\textbf{set-builder notation} enables us to create more complex definitions.

\begin{Def}[Set-Builder Notation]{def:set_builder}
    General form: $\{x \mid P(x)\}$,
    \begin{itemize}
        \item $x$ = defines some variable.
        \item $``\mid"$ = is short hand for ``such that.''
        \item $P(x)$ = describes the properties $x$ must satisfy.
    \end{itemize}
\end{Def}

\noindent
\textbf{For Example:} Lets Define the set of even integers\\
\vspace{-1em}
\begin{itemize}
    \item $\{x \mid x \textnormal{ is an even integer}\}$: ``$x$, such that, $x$ is an even integer.''
    \item $\{x \in \mathbb{Z} \mid x \textnormal{ is even}\}$: ``$x$ in Integers, such that, $x$ is an even.''
    \item $\{x \in \mathbb{Z} \mid x \textnormal{ is not odd}\}$: ``$x$ in Integers, such that, $x$ is not odd.''
\end{itemize}

\noindent
\underline{\textbf{It's important to Define exactly what variables are.}}
In the above, $x$ was stated directly as an integer. If not, x could be \underline{\textbf{water-balloons} or \textbf{puppies}.}
